Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-12-16 R0V0.tex
Item 8

\mypara For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general Lyapunov function is a non-trivial problem by itself \cite{MalisoffMazenc2009}. The case can be even worse, when structural constraints are considered.

>>>>

\mypara For nonlinear systems described by a non-fully connected graph, the design of structured controllers could be simplified by choosing structured control-Lyapunov functions (see \cite{Dirr2015} and references therein). However, the search for a general control-Lyapunov function is a non-trivial problem by itself (see \cite{MalisoffMazenc2009} for the search of Lyapunov functions). The case can be even worse, when structural constraints are considered.
